\documentclass[11pt]{article}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\usepackage{fontspec, graphicx}
\usepackage[dvipdfm, colorlinks, breaklinks, pdftitle={Stolen},pdfauthor={Loh, Adrian}]{hyperref}
\usepackage[usenames]{color}
\definecolor{Gray}{rgb}{.7,.7,.7}
\newcommand{\smallprint}[1]{\fontspec{Adobe Caslon Pro}\fontsize{10pt}{13pt}\color{Gray}\selectfont #1}
\newcommand{\ga}[1]{\fontspec[Ligatures={Common}]{Acanthus-Italic}\fontsize{46pt}{50pt}\selectfont #1}
%\usepackage{setspace}
%\doublespacing
\begin{document}
\begin{center}\ga{My Darling of Velocity}\end{center}
\begin{center}by Adrian Loh\end{center}

\section{} % (fold)
\label{sec:section_name}

	There had always been at that precipice in memory, a jubilation that I remember.
An elusive irrecoverable innocence that came simply as a by-product of youth. Of
ignorance. The blissful ferocity of those days, I remember them. I remember them
like a previous life I had lived and probed with every inch of my breath and my
being.

	We walked further along the embankment. A constant winter breeze started to blow
across the Main, chilled by the freezing waters.

	``It’s getting a bit cold.'' She said and wrapped her arms tighter around
herself.

	``Let’s turn off here.'' I said pointing to a small tunnel tucked in the middle
of an administrative building from the 16th century. The tunnel opened into a
piazza, with a galleria of bridal boutiques and a deserted cafe in the north
corner.

	We walked in silence for a while, passing storefronts with jewelry and gowns.
The solitary echoes of our footsteps resounding over the thousand-year old
cobblestone footpath. She told me she was eager to get on with her life and I
told her likewise. As we spoke, I saw her gaze fixate to a distance out in front
of her, as if she were gazing at an apparition of a future there.

	But perhaps fate had other plans for us that night, and that night an
incomprehensible silence befell upon us, like the dead silence that follows
after I felt the skin on the back of her hand as it brushed up against mine. A
space that contains the weight of history.

	That night, I gathered her into my eyes until it could no longer contain light.
Until every memory became a part of this tapestry I would weave from the shadows
of her laughter and her voice and our voices speaking to each other,
intermingled with the winter silence. My voice that has ever only known itself
speaking to her.

	Somewhere beyond the walls of the piazza, the shrill of microphone feedback
pierced the winter air, as music followed. She took my hand suddenly and started
to run.

	``Where’re we going?'' I asked as our steps hastened and the music grew clearer.

	``I don’t know. C’mon!'' She yelled at the verge of laughing.

	Our hands disentangled, and she raced on ahead of me as I tried to catch up. She
spun around ``C’mon, baby!'' she yelled and giggled. Then stopped and waited as
I caught up.

	``I’m getting too old for this shit.'' I said, stopping to catch a breath as the
cold mixed with the fire in my lungs.

	``No, you’re not...'' She said and laughed pushing her head onto mine. ``Come
on...'' She said softly, extending me her hand. I caught a breath, took her hand
and we ran.

	Beyond the wall, a crowd had gathered around a semi-lit stage up ahead. The band
played in a stagger, a few bars and they would stop to tune their guitars before
continuing to play again. The lead singer screamed unintelligible German lyrics
and varied his pitch with every restart. She moseyed her way up to a guy who
towered over her, standing at the edge of the crowd. I watched them speak for a
moment, and she came back to tell me they were doing a soundcheck of some sort
for a concert tomorrow.

	The lead singer turned to his band, ``Von der Spitze'' he murmured. One of the
guitarist said something in reply and they laughed among themselves. They got
ready again and began to play. This time, they didn’t stop, and the music
blasted into the night. The people who had gathered around started to dance
in-place, their spastic movements restricted by the thick coats and winter
jackets they had on.

	I stood at the periphery of the crowd and watched her slowly ease herself into
the center of the frenzy. My darling of velocity. A creature eternally propelled
by some strange invisible force towards the glare and the deafening, where the
lights always shined brightest and the music always played loudest. How I had
always watched her, my every silent gaze eternally clinging to her gravity at
the edge of that feverish universe spinning from origin to ash. Occasionally, I
would lose her in the facelessness and the movement. Occasionally, I would find
her again and she would turn to me and her lips would move to whisper something
indecipherable to me. I would whisper back. In the years between, I’d woken up
in tears sweating, drowned in a sea of sighs sifting for her face in that
faceless crowd. A love that closes its mouth before speaking her name. I know
what it’s like to harbor desire. I know what it’s like to murder it.

	She waved, beckoning me to go to her. I waded my way through the crowd towards
her. She smiled and turned away to look at the band, moving awkwardly to the
music as the music pounded into me. Tiny particles of snow had started to fall.
They glistened like crystals as they entered the strobes of stage lights beamed
into the night sky.

	She grabbed my hand when I was close enough and drew me next to her. I stood
still and faced the stage as she turned and leaned over to me.

	``You having fun?'' She screamed, smiling.

	``Yeah,'' I replied, and smiled.

	``Liar,'' she said and laughed and threw both her arms around me.

	There, in the weightless pools of her eyes, I saw reflected the history of the
world dissolve into this aching possibility

	The sudden realization of your soul that it has never before been recognized.

of one burning fleeting moment, and how we had believed then, to believe that
there is no thing that does not yearn, that you could shift the balance of the
world with the weight of your desires.

% section section_name (end)

\section{} % (fold)
\label{sec:section_name}

	``So what’s she like?'' She asked, ``Your wife.''

	A cloistered silence of bedrooms pregnant with the air of memory

	Looking back it was not the struggle that maimed us. It was this ambiguity we
threw punches at in the dark not knowing what we were attempting to strike,
whether or not it was struck. That our dreams of velocities were merely
illusions and distortions of the stillness we sought to find but were afraid of
in the beginning.

	The tailwinds of lovesighs and bedlaughter.

% section section_name (end)


\begin{flushright}\emph{Kuala Lumpur, 2007--2008}\end{flushright}

\end{document}

