\documentclass[11pt]{article}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\usepackage{fontspec, graphicx}
\usepackage[dvipdfm, colorlinks, breaklinks, pdftitle={Stolen},pdfauthor={Loh, Adrian}]{hyperref}
\usepackage[usenames]{color}
\definecolor{Gray}{rgb}{.7,.7,.7}
\newcommand{\smallprint}[1]{\fontspec{Adobe Caslon Pro}\fontsize{10pt}{13pt}\color{Gray}\selectfont #1}
\newcommand{\ga}[1]{\fontspec[Ligatures={Common}]{Adobe Garamond Pro}\fontsize{48pt}{50pt}\selectfont #1}
%\usepackage{setspace}
%\doublespacing
\begin{document}
\begin{center}\ga{Stolen}\end{center}
\begin{center}by Adrian Loh\end{center}

	--- I'd never gotten more pussy than when I moved into this address and 
bought that fucking car. 

	He says, and pours himself another drink. He could feel 
a vacuum form inside the apartment as his gaze drifted to the fluttering 
balcony curtains being sucked outwards. The dead air inside straining out into 
the cool subtropical night. Faintly, Cantonese techno, New Orleans jazz 
intermingled with the chatter of drunk crowds vacillated from the pubs 28 
floors below.

	He's hunched over the ceramic counter-top. Imported Italian sold by the square
inch excavated from ancient limestone and Paleolithic feces. More a bar counter
now than the breakfast island in the ``architectural visualizations'' of his once
demented domesticated fantasy. Eurasian paper children and a blonde plastic wife
in an \emph{Anna Sui} sundress and leather garters underneath. When the kids are
away, mummy gives it to daddy like a pornstar. One big happy gathered around
microwaved French toast and carton-boxed orange juice. Iridium embossed
stainless steel \emph{Westinghouse} fridge with an in-door ice-dispenser.
Humidity controlled. All 660 liters stuffed full of imported condiments for
``fusion'' recipes of dinners he Googled but will never cook. There were more wine
glasses in here now than plates and bowls, more fucking happened in here than
cooking.

	She's sprawled out on all fours on the floor in her underwear across the
room. He watches her from where he's sitting, making rhythmic clinks with the 
ice as he twirls them around inside the glass.

	--- Well it could be worse, honey.

	She says, hammering away at the perfect white lines of cocaine strewn 
neatly on a mirror with a century-old apricot wooden frame. Oriental engravings 
of massive Turkish battles and orgies twice in number. Take the women, burn 
everything else. A genetic marker in the Y-Chromosome of over 16 million men 
living today scattered across a region stretching from China to the Middle East 
have been linked as directly descending from Genghis Kahn. The tyrant lover 
liked girls with small noses, rounded hips, long silky hair, red lips and 
melodious voices and he measured their beauty in carats: if they were rated 
below a certain number, they were sent away to be shared amongst his officers. 
An entire bloodline of rape-victim barstards marching to the playlists of Total 
Request Live and clinging to the scrolling marquees of Wall Street for dear 
life.

	--- Too much of anything will kill you eventually.

	She says, then arches her neck down, takes a long drag of the powder,
nostrils pushed to the glass, then whiplashes up for oxygen. Her long, straight 
hair cutting an arc through the air. On all fours, she looks like a spastic 
caricature of a neon sign from a Thai A-Go-Go nightclub. \emph{Super Pussy. No Cover 
Charge.} Dull lap dances and even duller blowjobs for the price of a stick of 
gum and a green card. \emph{Bada-bing}, he thought and smiles to himself.

	She slings herself over the leather bean-bag as nirvana raced through her 
neurons. Her arms draped to her sides, hands extended like some mannequin of 
Virgin Mary in \emph{Victoria's Secret} offering to dish out handjobs for peace and 
goodhead to all men.

	The apartment had ``convenient access to some great schools'', an unsurpassed
view (before the developer went and built another six blocks in front of this 
one). A major shopping mall --- major in this city that inaugurates shopping 
malls like national monuments --- was a ten-minute drive away (if they opened 
after midnight and you liked shopping at four in the morning).

	He takes a swig from the glass, then refills it half-way. He rises from the 
stainless steel stool, feels the buzz settling in his brain. He walks, steady 
still, to the threshold of the balcony. He leans on the sliding door, feeling a 
slight draft beneath his robe. Where once he could see the Towers, now he saw 
only the dense halo of illuminated clouds above them on those nights when 
electricity was scarce but some visiting dignitary had to be treated to a 
masturbation of lights before lifting the trade embargo on underage sex 
workers. They'll flip the razzle dazzle switch on the Towers and you swear at 
that very moment, under the electrical buzz of the spotlights, you can hear the 
collective whining of some brokeass squatter community as Manchester United and 
Chelsea flickered into black on their dead television screens. Negligible 
minority discontentment in exchange for these monuments of a civilization that 
premature-ejaculated on itself and swallowed up every last drop of its 
children's dreams.

	--- Well, this is the life as they say.

	He says and takes a sip, as his eyes darted across the isolated pigeon 
holes of lamplight from the apartment block in the distance.

	--- Who says that?

	She asks in a throaty voice, head arched over the cliff of the bean-bag.

	--- We used to say that.

	He remembered, when the other six blocks went up, it was as if someone had 
snuck in while he was on a business trip to Macau charging threesomes to his 
expense account, removed the postcard he had paid 1.2 million ringgit to behold 
while getting his cock sucked and replaced it with a paralytic grid of Haier 
air-conditioning units and retrofitted satellite dishes and called it 
postmodern Asian art. Telephoto lenses would've come in handy at that point, if 
only your inter-apartment neighbors were ever away from their offices long 
enough to come home and fuck. 

	Here we are, he thought downing the last of the whisky, dancing on the very 
edge of globalization, waiting for the end of days when we'll all be caught 
bent over the hood of an electric car with our knickers around our ankles and 
our faces pressed up against an inflating barrel of crude oil.

	With some effort, she arches her body up, then looks directly at him and 
spreads her legs.

	--- Birthday suck off.

	She asks.

	--- What're you doing all propped up?

	He asks.

	--- \emph{Waiting for you to come over here and stick your dick in my mouth}.

	She says. He laughs. She laughs. 

	--- Baby, come here.

	She says quietly, almost sweetly, holding his gaze for a moment before
sinking her head back into the leather.

	He makes a beeline towards her, watching her sprawled there and knowing his 
penis was as soft as her insides. No penetration without plunder. A 
protein-supplement induced comatosed prick brought on by too much running on 
treadmills, eating organic by day and drowning in a sea of cunt juices and Jack 
Daniel's by night. \emph{Abercrombie \& Fitch} hamsters getting high on their own 
reflections.

	--- My brain feels like cunt. 

	He says and they laugh as he takes the last few strides towards her before 
collapsing beside her.

	She sinks to her knees, wraps her mouth around his limp cock. His cock
still in her mouth, she starts massaging his balls with the ice.

	He was now a part of the machine. A mechanism in a stuttering engine with 
21 million moving parts. He knew that. And it made him almost want to throw up 
all over her perfect skin. The engine that had grafted itself onto him and 
there was no way to surgically sever it. He thought of his heart, the pulmonary 
vena cava clogged by the stone walls he'd erected over the years. His heart 
strangled in a mesh of barbwire. A heart collapsing from the weight of its own 
desires.

	She turns to her side, scoops a line off the mirror with the folded 
cardboard, lays flat again. Then meticulously, with the concentration of a 
brain surgeon, she taps the white powder out, creating a circle of white sand 
around the monolith that was the nipple of her right breast.

	He sinks in and snorts, and for a moment thought, as fire went into his 
left nostril while her nipple was lodged into his right, at every step we had 
to invent something greater, imitate a grander lie, up the dosage, push 
ourselves that much closer to the brink of no return, the precipice from which, 
looking back, we had no true desire to return from.

	He licks the remaining traces off her breast, snaps his head back as the 
fire meets his blood. She laughs as his head lands to rest on her belly. He 
feels the tremor of her laughter reverberate through his jaw. He looks up at 
her. At her smiling at him, perfectly framed between her breasts like the 
mounds of two symmetrical eggs. The view you get when you're busy chewing cunt. 
Anthropologists have proposed that the swell of female breasts is equivalent to 
the swollen fertile buttocks of our primate ancestors. Theories suggest that 
the evolution of breasts is related to sexual intercourse changing from the 
male mating from the rear to front-to-front contact. If it weren't for breasts, 
you'd never see his face.

	--- It'll all be over soon. I promise.

	She says. Her voice enters him through her stomach. His face pressed 
against her cave of echo and reverberation, as if he were listening to her 
underwater.

	--- Will it really?

	He asks.

	--- M-hm.

	But it was these contrivances that drove him. The apartment, the cars, the 
booze and the broads. The sheer ferocity of our devices of lies. That sustain 
life. Our fears that clutch and grip and claw at our skins and our dreams. Our 
becoming that instigates our unbecoming. Our birth our diminishing. You never 
grow or mature, you only learn to mistrust your own lies. You could make it all 
disappear, he thought, if only you wished hard enough, like Dorothy clicking 
her red heels until warm yellow pee ran down her legs. There's no place like 
home. There's no place like home. There's no place like sinking your face into 
Dorothy's curls and going to sleep forever.

	--- I could shit myself on these dreams.

	He laughs suddenly. On the one-way express to nowhere with no coming back 
and visiting hours are over. Resting on her skin as the fire simmered into a 
warmth at the back his skull, he could feel it, a slow sinking realization like 
rising nausea. He could see it all then, spread out before him like a 
production line for sex toys of Vaseline coated apple-bottoms lined in 
succession waiting for his eternal hard-on: the promise of a decade of 
loneliness.

	--- You're really ranting tonight, huh?

	She says, stroking his hair gently like some misplaced lover would've have 
in some imagined life. she had been his plastic wife and they would've had 
their paper children and served them Greek tequila and home-grown joints for 
breakfast. Not that commercial shit you get off the shelf but the hearty 
wholesomeness from mummy's own bushes. They'd send the kids off to school and 
spend the rest of the day fucking, and just as he's about to erupt on her face, 
a call would interrupt from the PTA telling them that daddy's little squirt was 
caught chugging ants down the blouse of a girl twice his age so he could watch 
her frantically undress and reveal the secrets of the universe to him.
	
	--- It's this fucking place.
	
	He says. Building egos the size of shopping malls under flash-photography 
and acid rain, drilled into a bedrock of political monarchy and delusional 
economic policies. Breakfast at Tiffany's shrouded in a mist of bottle-necked 
congestion and tropical haze and that terrifying feeling that we are not quite 
ever going to get there no matter how well we imitate.

	--- Maybe we should go somewhere after all this. Been a while since we've 
gone anywhere. 

	She says.

	--- Maybe India.
	
	She continued in a whisper. State reason for visit: to find my heart 
Charka. But he knew it was useless. He'd accepted that. You can never trust 
happiness. Not the happiness you find or create, or the happiness that stumbles 
upon you like sudden morning rain. You never denounce faith, you merely 
accumulate pain. You only fill your wells of absence. Vacation photos 
accompanied by the digital timestamps of longing. Every mundane moment 
immortalized on some clit-sized Memory Stick and then uploaded onto some blog 
whose colors match your mood. 

	The history books of the future will contain neither the names of people 
nor the dates of events. It will be a faceless, nameless Dystopia of the every 
day, of how a girl from a Wi-Fied village in Africa was Eiffel Towered by two 
boys in her tribe last night and how the teenager living next door got his 
first erection watching his slutty aunt take a pee. It will be a crescendo of 
heartaches strung like origami cranes across the wobbly threads of the World 
Wide Web, the voices of young men calling their ex-girlfriends ``cocksucker'' in 
26 languages and animated 3D-holograms of 16-year old girls showing off their 
birthday boob-jobs to hip-hop music in front of Logitech webcams. An entire 
generation with self-esteems fibre-optically tethered to the number of ``Now 
Online'' people they will never see or give a shit enough to pick up a phone to 
call, hunched over their Macbooks every night ranting on every conspiring 
detail so that others may find comfort in knowing we are all part of this 
collective shitpile of random tragedies. An aborted generation of has-beens 
long before we ever were.

	--- And where's the girl next door?

	He asked quite suddenly, getting up on his knees. 

	--- Where's she in all this?

	--- You didn't ask me to bring a friend.

	She says and he laughs. She slips one leg between his legs and starts 
rubbing his partial erection through the robe with her feet.

	--- I'd always wanted a girl next door growing up.

	--- I'd always wanted to get my Barbie a Dream House...

	She eases his robe apart. 
	
	--- What's your point?
	
	He removes her feet from his crotch, brings her legs up to his shoulders 
before sinking his body entirely between them, inhaling up along the insides of 
her thighs.	

	--- While you're down there...

	She giggles, biting the side of her lips.

	Head between her legs, he stretches one arm out towards the mirror, taps 
blindly on the mountain of powder. Then, finger covered in white, he smears the 
powder into her gaping cunt and sinks his mouth into it.

	Here, nested in her darkness of tastes and smells, he wanted to disappear 
completely forever, engulfed by the mouths of her buried cities and her lost 
languages of sighs. Now every fucking thing in life worth living for was over, 
cause we'd smoked all the good shit and drank till the spirits dried and our 
spirits died. Wrap your fucking lips around this, the monumental erection of my 
aborted dreams. And suck hard.

	--- All the good ones are going or gone.

	He said, resting next to her, his lungs palpitating like a dying fire 
gasping for air.

	--- But we had a good run. We gave the bitch a shot, and she fucking blew 
it. Blew it like she was suffocating and there was oxygen in his balls. The 
precious fucking illusion of it all.

	She laughs, half breathless.

	\begin{flushright}\emph{Kuala Lumpur, 2007--2008}\end{flushright}

\end{document}

